A linear inside-outside algorithm for correcting sequencing errors in structured RNA sequences

### 2012-10-07 Recomb/results_RECOMB.tex
conclusion

@@

\begin{figure}
\begin{subfigure}[b]{0.3\textwidth}
\includegraphics[width=1.2\textwidth]{figures/ROC_6.pdf}
\caption{6 mutations}
\label{fig:ROC6mut}
\end{subfigure}
\hfill
\begin{subfigure}[b]{0.3\textwidth}
\includegraphics[width=1.2\textwidth]{figures/ROC_12.pdf}
\caption{12 mutations}
\label{fig:ROC12mut}
\end{subfigure}
\hfill
\begin{subfigure}[b]{0.3\textwidth}
\includegraphics[width=1.2\textwidth]{figures/ROC_24.pdf}
\caption{24 mutations}
\label{fig:ROC24mut}
\end{subfigure}
\caption{Performance of error-correction. The row index indicates the number of mutations performed with \RNApyro, and the column index indicates
the value of the parameter $\alpha$ distributing the weights of stacking pair energies vs isostericity scores. In each cell, we report the average AUC
values over the 10 experiments.}
\label{fig:ROCall}
\end{figure}

@@

\subsection{Time}
Further NGS applications of \RNApyro implies a need for efficiency and scalability. In Table~\ref{tab:time} we
present different times needed to compute the probabilities for  every nucleotide at every positions for a vast set of parameters. For those test
 all the sequences were generated randomly, as the target secondary structure.

\begin{table}
\begin{center}
\begin{tabular}{lccc}
$|s|$&\multicolumn{3}{c}{Number of mutations}\\\cline{2-4}
		 			  & 6   &  12  & 24\\\cline{2-4}
100  				& 35s  & 238s & 1023s\\
300  			& 135s & 594s &2460s\\\cline{2-4}
		 						& 25   & 30   &			\\\cline{2-4}
300       &      &  3950s&     \\
500         & 5400s&       &      \\
\end{tabular}
\end{center}
\caption{Time to compute all probabilities. The first column indicates the length and  the column indexes indicate the number
 of mutations. $\alpha$ is
set at $0.5$, and $\beta=1.5$ and $|\Omega|=44$.}
\label{tab:time}
\end{table}

>>>>

The time benchmarks were done on a MacBook Pro 2010, 2 processors at 2.66GHz, 8GB of RAM.
Since applications of \RNApyro implies a need for
 efficiency and scalability. In Table~\ref{tab:time} we
present different times needed to compute the probabilities for  every nucleotide at every positions for a vast set of parameters. For those test
 all the sequences were generated randomly, as the target secondary structure.

\begin{table}
\begin{center}
\begin{tabular}{lccc}
$|s|$&\multicolumn{3}{c}{Number of mutations}\\\cline{2-4}
		 			  & 6   &  12  & 24\\\cline{2-4}
100  				& 35s  & 238s & 1023s\\
300  			& 135s & 594s &2460s\\\cline{2-4}
		 						& 25   & 30   &	50		\\\cline{2-4}
300       &      &  3950s&     \\
500         & 5400s&       &  21003s    \\
\end{tabular}
\end{center}
\caption{Time to compute all probabilities. The first column indicates the length and  the column indexes indicate the number
 of mutations. $\alpha$ is
set at $0.5$,  $\beta$ to $1.5$ and $|\Omega|=44$.}
\label{tab:time}
\end{table}

@@

\begin{figure}
\begin{subfigure}[b]{0.3\textwidth}
\includegraphics[width=1.2\textwidth]{figures/ROC_6.pdf}
\caption{6 mutations}
\label{fig:ROC6mut}
\end{subfigure}
\hfill
\begin{subfigure}[b]{0.3\textwidth}
\includegraphics[width=1.2\textwidth]{figures/ROC_12.pdf}
\caption{12 mutations}
\label{fig:ROC12mut}
\end{subfigure}
\hfill
\begin{subfigure}[b]{0.3\textwidth}
\includegraphics[width=1.2\textwidth]{figures/ROC_24.pdf}
\caption{24 mutations}
\label{fig:ROC24mut}
\end{subfigure}
\caption{Performance of error-correction. Subfigures accuracy with under-estimated error rate (6 mutations), exact estimates (12 mutations) and over estimates 
(24 mutations). We also analyze the impact of the parameter $\alpha$ distributing the weights of stacking pair energies vs isostericity scores and use values 
ranging of $\alpha=\{0,0.5,0.8,1.0\}$. The AUC is indicated in the legend of the figures. Each individual ROC curve represent the average performance aver the 10 experiments.}
\label{fig:ROCall}
\end{figure}

@@
